\section{Related Work}
\label{sec:related}

In this section, we cover relevant studies in machine learning models and data analyses.

\textbf{Models.}
A plethora of machine learning models has been studied to improve prediction results as well as data analyses.
Linear regression~\cite{linear} is a linear approach to model the relationship between a response and a set of variables.
Logistic regression~\cite{logistic} is a process of modeling the probability of a discrete outcome given an input variable.
Decision tree~\cite{decisiontree} is a tree-like model that supports making decisions by classifying attributes.
K-nearest neighbors (KNN) algorithm~\cite{knn} is a non-parametric learning method that predicts a response based on the aggregation of the characteristics of nearest neighbors.
Bayesian network~\cite{bayesian} is a probabilistic graphical model that represents a set of variables and their conditional dependencies via a directed acyclic graph (DAG).
Support vector machine (SVM) algorithm~\cite{svm} is a model to find a hyperplane in a multi-dimensional space that distinctly classifies the data points.
Neural network~\cite{neuralnetwork} is a series of algorithms that recognizes underlying relationships in a set of data through a process that mimics the way the human brain operates.
K-means clustering~\cite{kmeans} aims to partition observations into $K$ clusters in which each observation belongs to the cluster with the nearest mean.

\textbf{Analysis studies.}
The models mentioned above are actively utilized for predicting responses in various fields such as health care, medical diagnosis, weather condition, and image recognition.
Tian et al.~\cite{health_nn} presents a recurrent neural network model, developed for health condition prediction of gearboxes based on the vibration data collected from a gearbox experimental system.
Hoppner et al.~\cite{imagerecognition} discusses the methods for classification, and image and pattern recognition with fuzzy data.
Kononenko et al.~\cite{medicaldiagnosis} provides an overview of the development of intelligent data analysis in medical diagnosis, and presents a comparison of representative systems.